Evaluation of probabilistic photometric redshift estimation approaches for \boldblue{ \textsc{The Rubin Observatory Legacy Survey of Space and Time} (LSST)}

### 2020-09-02 paper/authors.tex

\author[LSST Dark Energy Science Collaboration]{
\parbox{\textwidth}{
\Large
S.J.~Schmidt$^{1}$,
A.I.~Malz$^{2,3,4}$,
J.Y.H.~Soo$^{5,6}$,
I.A.~Almosallam$^{7,8}$,
M.~Brescia$^{9}$,
S.~Cavuoti$^{9,10}$,
J.~Cohen-Tanugi$^{11}$,
A.J.~Connolly$^{12}$,
J.~DeRose$^{13,14,15,16,17}$,
P.E.~Freeman$^{18}$,
M.L.~Graham$^{12}$,
K.G.~Iyer$^{19,20}$,
M.J.~Jarvis$^{21,22}$,
J.B.~Kalmbach$^{12}$,
E.~Kovacs$^{23}$,
A.B.~Lee$^{18}$,
G.~Longo$^{10}$,
C.B.~Morrison$^{12}$,
J.A.~Newman$^{24}$,
E.~Nourbakhsh$^{1}$,
E.~Nuss$^{11}$,
T.~Pospisil$^{18}$,
H.~Tranin$^{11}$,
R.H.~Wechsler$^{25,16,26}$,
R.~Zhou$^{15,24}$,
R.~Izbicki$^{27,28}$,
and The LSST Dark Energy Science Collaboration
}
\vspace{0.4cm}
\\
\parbox{\textwidth}{
(Affiliations are listed at the end of the paper)
\vspace{0.8cm}
}
}

>>>>

\author[LSST Dark Energy Science Collaboration]{
\parbox{\textwidth}{
\Large
S.J.~Schmidt$^{1}$,
A.I.~Malz$^{2,3,4}$,
J.Y.H.~Soo$^{5,6}$,
I.A.~Almosallam$^{7,8}$,
M.~Brescia$^{9}$,
S.~Cavuoti$^{9,10}$,
J.~Cohen-Tanugi$^{11}$,
A.J.~Connolly$^{12}$,
J.~DeRose$^{13,14,15,16,17}$,
P.E.~Freeman$^{18}$,
M.L.~Graham$^{12}$,
K.G.~Iyer$^{19,20}$,
M.J.~Jarvis$^{21,22}$,
J.B.~Kalmbach$^{12}$,
E.~Kovacs$^{23}$,
A.B.~Lee$^{18}$,
G.~Longo$^{10}$,
C.B.~Morrison$^{12}$,
J.A.~Newman$^{24}$,
E.~Nourbakhsh$^{1}$,
E.~Nuss$^{11}$,
T.~Pospisil$^{18}$,
H.~Tranin$^{11}$,
R.H.~Wechsler$^{25,16,26}$,
R.~Zhou$^{15,24}$,
R.~Izbicki$^{27,28}$
\begin{center} (LSST Dark Energy Science Collaboration) \end{center}
}
\vspace{0.4cm}
\\
\parbox{\textwidth}{
(Affiliations are listed at the end of the paper)
\vspace{0.8cm}
}
}

### 2020-09-02 paper/tex/methods.tex
add Wolf 2009 reference and corresponding sentence

In this study, we used \annz-v.2.0.4 to output only the result of the ANN algorithm.
\Pzpdf s were produced by running an ensemble of 5 ANNs with a $6:12:12:1$ architecture corresponding to the 6 $ugrizy$ inputs, 2 hidden layers with 12 nodes each, and 1 output of redshift.
Each of the five ANNs was trained with different random seeds for the initialization of input parameters, reserving half of the training set for validation to prevent overfitting.
\boldblue{Galaxies not detected in the $u$-band} \sout{Undetected galaxies} were excluded from the training set, and per-band non-detections in the test set were replaced with the mean magnitude \boldblue{of the test set} in that band. \sout{within the entire test set.}

@@

The colour-matched nearest-neighbours photometric redshift estimator \citep[\cmnn,][]{Graham:17} uses a training set of galaxies with known redshifts that has equivalent or better photometry than the test set in terms of quality and filter coverage.
For each galaxy in the test set, \cmnn\ identifies a colour-matched subset of training galaxies using a threshold in the Mahalanobis distance $D_M = \sum_{j}^{N_{\mathrm{colours}}} (c_{\mathrm{j,train}} - c_{\mathrm{j,test}})^{2} / \delta c_{\mathrm{j,test}}^2$ in the space of available colours $c$, with colour measurement errors $\delta c_{\mathrm{test}}$ and $N_{\mathrm{colours}} = 5$ colours $j$ defined by the $ugrizy$ filters, which defines the set of colour-matched neighbours based on a value of the percent point function (PPF).
As an example, for $N_{\mathrm{filt}}=5$ with PPF$=0.95$, $95$ per cent of all training galaxies consistent with the test galaxy will have $D_M < 11.07$.
Undetected bands are dropped, thereby reducing the effective $N_{\mathrm{filt}}$ for that galaxy.
The \pzpdf\ of a given test set galaxy is the normalized distribution of redshifts of its colour-matched subset of training set galaxies.

>>>>

In this study, we use \annz-v.2.0.4.  \boldblue{Several combinations of the ANN, BDT, and kNN machine learning algorithms were tested during the training/validation stage.  For this particular dataset, the optimal and most stable results came from a setup consisting solely of ANNs.  We present results for this case and do not include results from a mixture of multiple algorithms. }
\sout{to output only the result of the ANN algorithm.}
\Pzpdf s were produced by running an ensemble of 5 ANNs with a $6:12:12:1$ architecture corresponding to the 6 $ugrizy$ inputs, 2 hidden layers with 12 nodes each, and 1 output of redshift.
Each of the five ANNs was trained with different random seeds for the initialization of input parameters, reserving half of the training set for validation to prevent overfitting.
\boldblue{Galaxies not detected in the $u$-band} \sout{Undetected galaxies} were excluded from the training set, and per-band non-detections in the test set were replaced with the mean magnitude \boldblue{of the test set} in that band. \sout{within the entire test set.}

@@

The colour-matched nearest-neighbours photometric redshift estimator \citep[\cmnn,][]{Graham:17} uses a training set of galaxies with known redshifts that has equivalent or better photometry than the test set in terms of quality and filter coverage.
For each galaxy in the test set, \cmnn\ identifies a colour-matched subset of training galaxies using a threshold in the Mahalanobis distance $D_M = \sum_{j}^{N_{\mathrm{colours}}} (c_{\mathrm{j,train}} - c_{\mathrm{j,test}})^{2} / \delta c_{\mathrm{j,test}}^2$ in the space of available colours $c$, with colour measurement errors $\delta c_{\mathrm{test}}$ and $N_{\mathrm{colours}} = 5$ colours $j$ defined by the $ugrizy$ filters, which defines the set of colour-matched neighbours based on a value of the percent point function (PPF).
As an example, for $N_{\mathrm{filt}}=5$ with PPF$=0.95$, $95$ per cent of all training galaxies consistent with the test galaxy will have $D_M < 11.07$.
\sout{Undetected bands} \boldblue{Bands in which the galaxy is not detected} are dropped, thereby reducing the effective $N_{\mathrm{filt}}$ for that galaxy.
The \pzpdf\ of a given test set galaxy is the normalized distribution of redshifts of its colour-matched subset of training set galaxies.

### 2020-09-02 paper/tex/results.tex

The values of the CDE loss statistic of individual \pzpdf\ accuracy are provided in Table~\ref{tab:cdeloss}.
It is worth noting that strong performance on the CDE loss, corresponding to lower values of the metric, should imply strong performance on the other metrics, though the inverse is not necessarily true.
Thus the CDE loss is the most effective metric for generic science cases.

>>>>

The values of the CDE loss statistic of individual \pzpdf\ accuracy are provided in Table~\ref{tab:cdeloss}.
\boldblue{Even in the absence of knowledge of the true underlying distribution the CDE loss can be determined up to a constant, thus the relative values provide a quantitative measure of code performance.}
It is worth noting that strong performance on the CDE loss, corresponding to lower values of the metric, should imply strong performance on the other metrics, though the inverse is not necessarily true.
Thus the CDE loss is the most effective metric for generic science cases.
